Case Study: RNA-Seq Differential Analysis

### 2018-02-22 datasets/RNA-Seq/RNA-Seq.Rmd
Run RNA-Seq case on cluster

## set up parallel backend
multicoreParam <- MulticoreParam(workers = 2)
```

@@

```{r}
bd <- initializeBenchDesign()
sb <- buildBench(bd, data = geneExp, parallel = TRUE)
```

>>>>

## set up parallel backend
cores <- as.numeric(Sys.getenv("SLURM_NTASKS"))
multicoreParam <- MulticoreParam(workers = cores)
```

@@

```{r}
bd <- initializeBenchDesign()
sb <- buildBench(bd, data = geneExp)
```
